\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-04-24 doc/incertae_sedis.tex
Remove duplicate definition of rooted splits.

In order to apply supertree methods to rooted trees with \emph{incertae sedis}
taxa, we first propose a semantics of \emph{incertae sedis }in terms of rooted
splits. We define rooted splits by noting that each edge of a tree divides the
tip taxa $\mathcal{L}$ into two groups: the include set $\mathcal{I}(e)$ which does not contain the root,
and the exclude set $\mathcal{E}(e)$ which does contain the root. Such a split may be written
\[
\mathcal{I}(e)|\bullet\mathcal{E}(e).
\]
where the $\bullet$ indicates the root. If no taxa are \emph{incertae sedis}, then the
exclude set for a node is just the total tip set minus the include set for the
node: $ \mathcal{E}(n) =\mathcal{L}-\mathcal{I}(n)$.

For a node $n$ on the tip-ward side of an edge $e$, we may also write $\mathcal{I}(n)$ for $\mathcal{I}(e)$,
and $\mathcal{E}(n)$ for $\mathcal{E}(e)$.

For any two rooted splits $A=A_{1}|\bullet A_{2}$ and $B=B_{1}|\bullet
B_{2}$ , we say that $A$ \emph{displays }$B$ if $B_{1}\subseteq A_{1}$
and $B_{2}\subseteq A_{2}$.

>>>>

In order to apply supertree methods to rooted trees with \emph{incertae sedis}
taxa, we first propose a semantics of \emph{incertae sedis }in terms of rooted
splits.
